
```{r, echo = FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.height = 6,
  fig.path = "figs/",
  echo = TRUE
)

```


[![Travis-CI Build Status](https://travis-ci.org/reconhub/recon.ui.svg?branch=master)](https://travis-ci.org/reconhub/recon.ui)

[![Coverage status](https://ci.appveyor.com/api/projects/status/98263wear2w7h1tp/branch/master?svg=true)](https://ci.appveyor.com/project/thibautjombart/recon.ui/branch/master)

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/recon.ui)](https://cran.r-project.org/package=recon.ui)

[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/recon.ui)](https://cran.r-project.org/package=recon.ui)


<br>

# Installing the package

To install the current stable, CRAN version of the package, type:
```{r install, eval=FALSE}
install.packages("recon.ui")
```

To benefit from the latest features and bug fixes, install the development, *github* version of the package using:
```{r install2, eval=FALSE}
devtools::install_github("reconhub/recon.ui")
```

Note that this requires the package *devtools* installed.



<br>

# What does it do?





<br>

# Resources

<br>



# Contributors (by alphabetic order):
- [Thibaut Jombart](https://github.com/thibautjombart)

See details of contributions on:
<br>
https://github.com/reconhub/recon.ui/graphs/contributors


Contributions are welcome via **pull requests**.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

**Maintainer:** Thibaut Jombart (thibautjombart@gmail.com)
